---
title: "Maestría en Estadística Aplicada<br>Manejo y Visualización de Datos"
subtitle: "Trabajo final"
author: Lic. Qca. Laura Carrau
format: 
  html:
    embed-resources: true
execute:
    echo: true
    warning: false
    message: false
editor: source
toc: true
lang: es
lightbox: true
---

## Introducción

El conjunto de datos seleccionado contiene información del catálogo de libros de Open Library ([Open Library](https://openlibrary.org/ "Un recurso de Internet Archive")).

Criterios de selección:

filter(author != "Author not available"

& description != "No description available"

& genres != "\['Subject not available'\]"

& genres != "\['Coloring books'\]"

& average_rating != 0.00

& num_pages != 0

& rating_count \> 10

Descripción del conjunto de datos

Tabla resumen de las variables y sus características

| Variable           | Descripción                        |
|--------------------|------------------------------------|
| book_id            | OpenLibrary Identifier             |
| title              | Book title                         |
| author             | Book author                        |
| description        | Book description                   |
| genres             | Book subjects                      |
| first_publish_year | Book first published year          |
| editions           | Number of editions                 |
| num_pages          | Number of pages                    |
| cover_m            | Link to cover's book - medium size |
| cover_l            | Link to cover's book - large size  |
| average_rating     |                                    |
| rating_count       |                                    |
| id_goodreads       |                                    |
| id_amazon          |                                    |

## Materiales y métodos

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

## Resultados

El análisis realizado mostró

## Conclusiones

muchas gracias
